---
title: "HW6"
author: "Brian Chang"
date: "2019/11/23"
output: html_document
---

```{r load relevant libraries, include=FALSE}
library(tidyverse)
library(mlbench)
library(caret)
library(pROC)
```

## Load Data

```{r}
data("PimaIndiansDiabetes")

PimaIndiansDiabetes[is.na(PimaIndiansDiabetes)] = 0

train_size = floor(0.75 * nrow(PimaIndiansDiabetes))
train_pos <- sample(seq_len(nrow(PimaIndiansDiabetes)), size = train_size)

train_classification <- PimaIndiansDiabetes[train_pos, ]
test_classification <- PimaIndiansDiabetes[-train_pos, ]
```

## Support Vector Machine with Linear Kernel

```{r}
set.seed(100)
control = trainControl(method = "repeatedcv", repeats = 5, classProbs = T, savePredictions = T)

svm = train(diabetes ~ .,  data = train_classification, method = "svmLinear", tuneLength = 10, trControl = control)

svm
```


```{r}
roc(predictor = svm$pred$pos, response = svm$pred$obs)$auc

plot(x = roc(predictor = svm$pred$pos, response = svm$pred$obs)$specificities, y = roc(predictor = svm$pred$pos, response = svm$pred$obs)$sensitivities, col= "blue", xlim = c(1, 0), type ="l", ylab = "Sensitivity", xlab = "Specificity")
```


```{r}
svm_test = predict(svm, newdata = test_classification)
confusionMatrix(svm_test, reference = test_classification$diabetes)
```

## Support Vector Machine with Radial Kernel

```{r}
set.seed(123)
control = trainControl(method = "repeatedcv", repeats = 5, classProbs = T, savePredictions = T)

svm_radial = train(diabetes ~ .,  data = train_classification, method = "svmRadial", tuneLength = 10, trControl = control)

svm_radial
```


```{r}
roc(predictor = svm_radial$pred$pos, response = svm_radial$pred$obs)$auc

plot(x = roc(predictor = svm_radial$pred$pos, response = svm_radial$pred$obs)$specificities, y = roc(predictor = svm_radial$pred$pos, response = svm_radial$pred$obs)$sensitivities, col= "blue", xlim = c(1, 0), type ="l", ylab = "Sensitivity", xlab = "Specificity")
```


```{r}
svm_radial_test = predict(svm_radial, newdata = test_classification)
confusionMatrix(svm_radial_test, reference = test_classification$diabetes)
```

## Simulated Annealing followed by Support Vector Machine
* We see that glucose and age were the two top variables selected and will use those in the support vector machine.
```{r}
sa_ctrl <- safsControl(functions = rfSA,
                       method = "repeatedcv",
                       repeats = 5,
                       improve = 50)
set.seed(10)
rf_sa <- safs(x = PimaIndiansDiabetes[,1:8], y = PimaIndiansDiabetes[,9],
              iters = 10,
              safsControl = sa_ctrl)
rf_sa
```

* Compared to the previous support vector machine with all predictors, this model performed with a lower accuracy.

```{r}
set.seed(321)
control = trainControl(method = "repeatedcv", repeats = 5, classProbs = T, savePredictions = T)

svm_feature = train(diabetes ~ glucose + age,  data = train_classification, method = "svmLinear", tuneLength = 10, trControl = control)

svm_feature
```

* The AUC for this model is also lower than the previous model.

```{r}
roc(predictor = svm_feature$pred$pos, response = svm_feature$pred$obs)$auc

plot(x = roc(predictor = svm_feature$pred$pos, response = svm_feature$pred$obs)$specificities, y = roc(predictor = svm_feature$pred$pos, response = svm_feature$pred$obs)$sensitivities, col= "blue", xlim = c(1, 0), type ="l", ylab = "Sensitivity", xlab = "Specificity")
```

